\addtocounter{table}{-1}
\begin{longtable}{|l|p{0.8\textwidth}|}\hline
\textbf{Acronym} & \textbf{Description}  \\\hline

AD & Associate \gls{Director} \\\hline
AURA & \gls{Association of Universities for Research in Astronomy} \\\hline
Alert & A packet of information for each source detected with signal-to-noise ratio > 5 in a difference image during \gls{Prompt Processing}, containing measurement and characterization parameters based on the past 12 months of \gls{LSST} observations plus small cutouts of the single-visit, template, and difference images, distributed via the internet. \\\hline
Alert Production & The principal component of \gls{Prompt Processing} that processes and calibrates incoming images, performs \gls{Difference Image} Analysis to identify DIASources and DIAObjects, packages and distributes the resulting Alerts, and runs the Moving \gls{Object} Processing System. \\\hline
Archive & The repository for documents required by the \gls{NSF} to be kept. These include documents related to design and development, construction, integration, test, and operations of the \gls{LSST} observatory system. The archive is maintained using the enterprise content management system \gls{DocuShare}, which is accessible through a link on the project website www.project.lsst.org. \\\hline
Association Pipeline & An application that matches detected Sources or DIASources or generated Objects to an existing catalog of Objects, producing a (possibly many-to-many) set of associations and a list of unassociated inputs. Association Pipelines are used in \gls{Prompt Processing} after \gls{DIASource} generation and in the final stages of \gls{Data Release} processing to ensure continuity of \gls{Object} identifiers. \\\hline
Association of Universities for Research in Astronomy &  consortium of \gls{US} institutions and international affiliates that operates world-class astronomical observatories, \gls{AURA} is the legal entity responsible for managing what it calls independent operating Centers, including \gls{LSST}, under respective cooperative agreements with the \gls{National Science Foundation}. \gls{AURA} assumes fiducial responsibility for the funds provided through those cooperative agreements. \gls{AURA} also is the legal owner of the \gls{AURA} Observatory properties in Chile. \\\hline
CCD & \gls{Charge-Coupled Device} \\\hline
Center & An entity managed by \gls{AURA} that is responsible for execution of a federally funded project \\\hline
Charge-Coupled Device & a particular kind of solid-state sensor for detecting optical-band photons. It is composed of a 2-D array of pixels, and one or more read-out amplifiers. \\\hline
Commissioning & A two-year phase at the end of the \gls{Construction} project during which a technical team a) integrates the various technical components of the three subsystems; b) shows their compliance with ICDs and system-level requirements as detailed in the \gls{LSST} Observatory System Specifications document (\gls{OSS}, LSE-30); and c) performs science verification to show compliance with the survey performance specifications as detailed in the \gls{LSST} Science Requirements \gls{Document} (\gls{SRD}, LPM-17). \\\hline
Construction & The period during which \gls{LSST} observatory facilities, components, hardware, and software are built, tested, integrated, and commissioned. \gls{Construction} follows design and development and precedes operations. The \gls{LSST} construction phase is funded through the \gls{NSF} \gls{MREFC} account. \\\hline
DESC & Dark Energy \gls{Science Collaboration} \\\hline
DIASource & A \gls{DIASource} is a detection with signal-to-noise ratio greater than 5 in a difference image. \\\hline
DM & \gls{Data Management} \\\hline
DMS & \gls{Data Management Subsystem} \\\hline
DMTN & \gls{DM} Technical Note \\\hline
DR & \gls{Data Release} \\\hline
DRP & \gls{Data Release Production} \\\hline
DTN & Data Transfer Node \\\hline
Data Management & The \gls{LSST} Subsystem responsible for the \gls{Data Management System} (\gls{DMS}), which will capture, store, catalog, and serve the \gls{LSST} dataset to the scientific community and public. The \gls{DM} team is responsible for the \gls{DMS} architecture, applications, middleware, infrastructure, algorithms, and Observatory Network Design. \gls{DM} is a distributed team working at \gls{LSST} and partner institutions, with the \gls{DM} \gls{Subsystem Manager} located at \gls{LSST} headquarters in Tucson. \\\hline
Data Management System & The computing infrastructure, middleware, and applications that process, store, and enable information extraction from the \gls{LSST} dataset; the \gls{DMS} will process peta-scale data volume, convert raw images into a faithful representation of the universe, and archive the results in a useful form. The infrastructure layer consists of the computing, storage, networking hardware, and system software. The middleware layer handles distributed processing, data access, user interface, and system operations services. The applications layer includes the data pipelines and the science data archives' products and services. \\\hline
Data Release & The approximately annual reprocessing of all \gls{LSST} data, and the installation of the resulting data products in the \gls{LSST} Data Access Centers, which marks the start of the two-year proprietary period. \\\hline
Data Release Processing & Deprecated term; see \gls{Data Release Production}. \\\hline
Data Release Production & An episode of (re)processing all of the accumulated \gls{LSST} images, during which all output \gls{DR} data products are generated. These episodes are planned to occur annually during the \gls{LSST} survey, and the processing will be executed at the \gls{Archive} \gls{Center}. This includes Difference Imaging Analysis, generating deep Coadd Images, \gls{Source} detection and association, creating \gls{Object} and Solar System \gls{Object} catalogs, and related \gls{metadata}. \\\hline
Difference Image & Refers to the result formed from the pixel-by-pixel difference of two images of the sky, after warping to the same pixel grid, scaling to the same photometric response, matching to the same \gls{PSF} \gls{shape}, and applying a correction for \gls{Differential Chromatic Refraction}. The pixels in a difference thus formed should be zero (apart from noise) except for sources that are new, or have changed in brightness or position. In the \gls{LSST} context, the difference is generally taken between a visit image and template.  \\\hline
Difference Image Analysis & The detection and characterization of sources in the \gls{Difference Image} that are above a configurable threshold, done as part of \gls{Alert} Generation Pipeline. \\\hline
Differential Chromatic Refraction & The refraction of incident light by Earth's atmosphere causes the apparent position of objects to be shifted, and the size of this shift depends on both the wavelength of the source and its \gls{airmass} at the time of observation. DRC corrections are done as a part of DIA. \\\hline
Director & The person responsible for the overall conduct of the project; the LSST director is charged with ensuring that both the scientific goals and management constraints on the project are met. S/he is the principal public spokesperson for the project in all matters and represents the project to the scientific community, \gls{AURA}, the member institutions of \gls{LSSTC}, and the funding agencies. \\\hline
DocuShare & The trade name for the enterprise management software used by \gls{LSST} to archive and manage documents \\\hline
Document & Any object (in any application supported by \gls{DocuShare} or design archives such as PDMWorks or GIT) that supports project management or records milestones and deliverables of the \gls{LSST} Project \\\hline
FITS & \gls{Flexible Image Transport System} \\\hline
FIU & Florida International University \\\hline
Flexible Image Transport System & an international standard in astronomy for storing images, tables, and \gls{metadata} in disk files. See the \gls{IAU} \gls{FITS} Standard for details. \\\hline
Handle & The unique identifier assigned to a document uploaded to \gls{DocuShare} \\\hline
IAU & International Astronomical Union \\\hline
LDF & \gls{LSST} Data Facility \\\hline
LDM & \gls{LSST} \gls{Data Management} (\gls{Document} \gls{Handle}) \\\hline
LPM & \gls{LSST} Project Management (\gls{Document} \gls{Handle}) \\\hline
LSE & \gls{LSST} \gls{Systems Engineering} (\gls{Document} \gls{Handle}) \\\hline
LSST & Large Synoptic Survey Telescope \\\hline
LSSTC & \gls{LSST} Corporation. an Arizona 501(c)3 not-for-profit corporation formed in 2003 for the purpose of designing, constructing, and operating the LSST System. During design and development, the Corporation stewarded private funding used for such essential contributions as early site preparation, mirror construction, and early data management system development. During construction, \gls{LSSTC} will secure private operations funding from international affiliates and play a key role in preparing the scientific community to use the LSST dataset. \\\hline
MOPS & Moving \gls{Object} Processing System \\\hline
MREFC & \gls{Major Research Equipment and Facility Construction} \\\hline
Major Research Equipment and Facility \gls{Construction} & the \gls{NSF} account through which large facilities construction projects such as \gls{LSST} are funded \\\hline
Moving \gls{Object} Processing System & The Moving \gls{Object} Processing System (\gls{MOPS}) identifies new SSObjects using unassociated DIASources. \gls{MOPS} is part of the \gls{Science Pipelines}. \\\hline
NCSA & National \gls{Center} for Supercomputing Applications \\\hline
NSF & \gls{National Science Foundation} \\\hline
National Science Foundation & primary federal agency supporting research in all fields of fundamental science and engineering; \gls{NSF} selects and funds projects through competitive, merit-based review \\\hline
OSS & Observatory System Specifications; LSE-30 \\\hline
Object & In \gls{LSST} nomenclature this refers to an \gls{astronomical object}, such as a star, galaxy, or other physical entity. E.g., comets, asteroids are also Objects but typically called a Moving \gls{Object} or a Solar System \gls{Object} (SSObject). One of the \gls{DRP} data products is a table of Objects detected by \gls{LSST} which can be static, or change brightness or position with time. \\\hline
Operations & The 10-year period following construction and commissioning during which the \gls{LSST} Observatory conducts its survey \\\hline
Operations Rehersal & A data management system prototype project employing the same methods, tools, personnel, and technologies as the real system in order to introduce and validate new algorithms, functionality, and infrastructure. Previously referred to as a data challenge. \\\hline
PSF & Point Spread Function \\\hline
PST & \gls{Project Science Team} \\\hline
Project Manager & The person responsible for exercising leadership and oversight over the entire \gls{LSST} project; he or she controls schedule, budget, and all contingency funds \\\hline
Project Science Team & an operational unit within \gls{LSST} that carries out specific scientific performance investigations as prioritized by the \gls{Director}, the \gls{Project Manager}, and the \gls{Project Scientist}. Its membership includes key scientists on the Project who provide specific necessary expertise. The \gls{Project Science Team} provides required scientific input on critical technical decisions as the project construction proceeds \\\hline
Project Scientist & The principal scientific advisor to the \gls{LSST} \gls{Project Manager} to ensure that \gls{LSST} system specifications are appropriate for achieving the scientific goals of the project; the \gls{Project Scientist} also works closely with the \gls{Systems Engineering} group and chairs the \gls{LSST} Science Council \\\hline
Prompt Processing & The processing that occurs at the \gls{Archive} \gls{Center} on the nightly stream of raw images coming from the telescope, including Difference Imaging Analysis, \gls{Alert} Production, and the Moving \gls{Object} Processing System. This processing generates Prompt Data Products. \\\hline
QA & Quality Assurance \\\hline
SRD & \gls{LSST} Science Requirements; LPM-17 \\\hline
Science Collaboration & An autonomous body of scientists interested in a particular area of science enabled by the \gls{LSST} dataset, which through precursor studies, simulations, and \gls{algorithm} development lays the groundwork for the large-scale science projects the \gls{LSST} will enable.  In addition to preparing their members to take full advantage of \gls{LSST} early in its operations phase, the science collaborations have helped to define the system's science requirements, refine and promote the science case, and quality check design and development work. \\\hline
Science Pipelines & The library of software components and the algorithms and processing pipelines assembled from them that are being developed by \gls{DM} to generate science-ready data products from \gls{LSST} images. The Pipelines may be executed at scale as part of \gls{LSST} Prompt or \gls{Data Release} processing, or pieces of them may be used in a standalone mode or executed through the \gls{LSST} \gls{Science Platform}. The \gls{Science Pipelines} are one component of the \gls{LSST} \gls{Software Stack}. \\\hline
Science Platform & A set of integrated web applications and services deployed at the \gls{LSST} Data Access Centers (DACs) through which the scientific community will access, visualize, and perform next-to-the-data analysis of the \gls{LSST} data products. \\\hline
Software Stack & Often referred to as the \gls{LSST} Stack, or just The Stack, it is the collection of software written by the \gls{LSST} \gls{Data Management} Team to process, generate, and serve \gls{LSST} images, \gls{transient} alerts, and catalogs. The Stack includes the \gls{LSST} \gls{Science Pipelines}, as well as packages upon which the \gls{DM} software depends. It is open source and publicly available. \\\hline
Solar System \gls{Object} & A solar system object is an astrophysical object that is identified as part of the Solar System: planets and their satellites, asteroids, comets, etc. This class of object had historically been referred to within the \gls{LSST} Project as Moving Objects. \\\hline
Source & A single detection of an astrophysical object in an image, the characteristics for which are stored in the \gls{Source} Catalog of the \gls{DRP} database. The association of Sources that are non-moving lead to Objects; the association of moving Sources leads to Solar System Objects. (Note that in non-LSST usage "source" is often used for what \gls{LSST} calls an \gls{Object}.) \\\hline
Subsystem & A set of elements comprising a system within the larger \gls{LSST} system that is responsible for a key technical deliverable of the project. \\\hline
Subsystem Manager & responsible manager for an LSST subsystem; he or she exercises authority, within prescribed limits and under scrutiny of the Project Manager, over the relevant subsystem's cost, schedule, and work plans \\\hline
Systems Engineering & an interdisciplinary field of engineering that focuses on how to design and manage complex engineering systems over their life cycles. Issues such as requirements engineering, reliability, logistics, coordination of different teams, testing and evaluation, maintainability and many other disciplines necessary for successful system development, design, implementation, and ultimate decommission become more difficult when dealing with large or complex projects. Systems engineering deals with work-processes, optimization methods, and risk management tools in such projects. It overlaps technical and human-centered disciplines such as industrial engineering, control engineering, software engineering, organizational studies, and project management. Systems engineering ensures that all likely aspects of a project or system are considered, and integrated into a whole. \\\hline
US & United States \\\hline
algorithm & A computational implementation of a calculation or some method of processing. \\\hline
astronomical object & A star, galaxy, asteroid, or other physical object of astronomical interest. Beware: in non-LSST usage, these are often known as sources. \\\hline
metadata & General term for data about data, e.g., attributes of astronomical objects (e.g. images, sources, astroObjects, etc.) that are characteristics of the objects themselves, and facilitate the organization, preservation, and query of data sets. (E.g., a \gls{FITS} header contains \gls{metadata}). \\\hline
patch & An quadrilateral sub-region of a sky \gls{tract}, with a size in pixels chosen to fit easily into memory on desktop computers. \\\hline
pipeline & A configured sequence of software tasks (Stages) to process data and generate data products. Example: \gls{Association Pipeline}. \\\hline
shape & In reference to a Source or \gls{Object}, the \gls{shape} is a functional characterization of its spatial intensity distribution, and the integral of the \gls{shape} is the \gls{flux}. Shape characterizations are a data product in the \gls{DIASource}, \gls{DIAObject}, Source, and \gls{Object} catalogs. \\\hline
sky map & A sky tesselization for \gls{LSST}. The Stack includes software to define a geometric mapping from the representation of World Coordinates in input images to the \gls{LSST} \gls{sky map}. This tesselation is comprised of individual tracts which are, in turn, comprised of patches. \\\hline
stack & A record of all versions of a document uploaded to a particular \gls{DocuShare} handle \\\hline
tract & A portion of sky, a spherical convex polygon, within the \gls{LSST} all-sky tessellation (\gls{sky map}). Each \gls{tract} is subdivided into sky patches. \\\hline
transient & A \gls{transient} source is one that has been detected on a difference image, but has not been associated with either an \gls{astronomical object} or a solar system body. \\\hline
\end{longtable}
