\section{Introduction} \label{sec:intro}

LSST \gls{DM} conducted the first operations rehearsal from May 7$^{th}$ to 9$^{th}$ 2019.
The plan for the rehearsal was outlined in \citeds{LDM-643}, the main principle was to simulate
nominal operations with \gls{CCD} data flowing from Chile, being processed (calibrated) and having some quality
assurance done on it.
\citeds{LDM-643} details the procedure and personnel involved,
hence in this document  we give only a brief summary of what  happened in the rehearsal.


\section{The rehearsal \#1}

There was a short prep meeting on the Monday before the rehearsal started to make sure everything was in place.
\subsection{Setup and limitations} \label{sec:setup}

A set of raft data (simulated data from DC2) which intersected
intersect \gls{tract} 4849 \gls{patch} 2,2.  The datasets for each night are comprised
of "observations" from two bands (night1: r, i-bands;  night2: z, y-bands, night3: u, g-bands).

Processing is to run singleFrameDriver.py - this is still Gen2 butler.

The three \gls{DESC} DC2 data sets were transferred to a DTN\footnote{lsst-user@139.229.127.99} in Chile to act as the acquired data.
A cron job was installed to start a script\footnote{\url{https://github.com/womullan/opsforwarder}} to transfer the files to the receiving node in \gls{NCSA} \footnote{xfer.ncsa.illinois.edu}. Secure copy \texttt{(scp)}  was used to make the transfer under the user \texttt{womullan}.

In operations the transfer nodes should be automatically transferring data which shows up in an operations directory. The script was only for this exercise. The \gls{DTN} which was used is an \gls{FIU} machine not one of our final nodes and hence is not set up as we will for operations.

Ingest, processing and \gls{QA} were run on the full dataset once transferred not as each file arrived.

\subsubsection{Communications }


A Slack channel \href{https://lsstc.slack.com/messages/CJBSY6FUN}{\#ops-rehearal-1}  was created
for minor communications.

Daily telecon was held using bluejeans at 11:00PST with the agenda:
\begin{itemize}
\item Serio	Status on mountain (can tailor for what is actually happening right now and we can discuss how this looks in commissioning and operations). Andrew gives "mock" night report.
\item Gruendl 	Processing summary. How did ingest go. How did processing go.
\item MacArthur, Slater	Metrics/QA, what's in the logs, what can we say about the data. Summary plots and metrics. What is missing in our view. What can we add for next night?
\item Morganson	Issues, resolution. Did anything happen that we can fix for the next night

\item All	Plan for next night. What do we need to do to make sure next night works better (or as well).
\end{itemize}


\input{day1}
\input{day2}
\input{day3}


\section{Conclusion and lessons learned}\label{sec:conc}
Though there were some limitations in out setup (\secref{sec:setup}) this was still useful exercise.

One central issue that should be followed-up on in subsequent rehearsals are the \gls{QA} metrics to be gathered during prompt processing and that utilities to provide rollups/summaries.

Though in the telecon status was discussed it was not properly recorded in the google sheet for the day,
there was no designated minute taker an individuals did not necessarily add a summary. In operations such a status
report should probably be filled even before the meeting.



